
\documentclass{llncs}
\pagestyle{plain}
% XXX: Page numbering is not working with this either

\usepackage{times}
\usepackage{complexity}
\usepackage{url}
\usepackage{latexsym}
\usepackage[utf8]{inputenc}
\usepackage{framed}
\usepackage{natbib}
\usepackage{graphicx}
%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{verbatim}
%\usepackage{accents}
\usepackage{bm}
%\usepackage[normalem]{ulem}
%\setlength\titlebox{6.5cm}    % You can expand the title box if you
% really have to

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\title{Sequentially Composable Rational Proofs for Space Bounded Computations}

\author{}

\institute{}
\date{}

\begin{document}
\maketitle
\input{mycommands.tex}

%% Shortcuts specific to Composition
\newcommand{\protOne}{\pi^{L_2}_{1}}
\newcommand{\protTwo}{\pi_{2}}
\newcommand{\rewGap}{\Delta}
\newcommand{\STEP}{\function{STEP}}

\newcommand{\disTransc}{\tilde{\Tau}}


% Question: Come rendere l'abstract (e il paper) il piu' Eurocrypt-appetibile possibile?
% XXX: The abstract should be rewritten
\begin{abstract}
We present new protocols for the verification of {\em non-deterministic space bounded polytime computations} against a rational adversary.
For non-deterministic polytime computations in sublinear space our protocol requires only a verifier running in sublinear-time. Our protocols can be proven 
secure even when composed sequentially, a scenario where many previously proposed rational proofs fail. Our results are the first rational proofs not based on the circuit model of computation, and the first sequentially composable protocols for a well-defined language class. 
%Unlike previous rational protocols in literature, our protocol can be used for repeated delegations when the computation is costly for the prover. % XXX: %Citations to be included?
\end{abstract}


% -- BEGIN Old abstract --
\begin{comment}
\begin{abstract}
This paper presents new protocols for the verification of {\em non-deterministic space-bounded polytime computations} against a rational adversary. More specifically consider a language $L \in \NTISP(T(n), S(n))$, i.e. a language recognized by a non-deterministic Turing Machine $M_L$ which runs in time $T(n)$ and space $S(n)$. 
We construct a protocol where a rational prover can
convince the verifier that $x \in L$ with the following properties: 
\begin{itemize}
\item The verifier runs in time $O(S(n) \log n)$;
\item The protocol terminates in $O(\log n)$ rounds and communication complexity $O(S(n) \log n)$;
\item The prover simply runs $M_L(x)$ and stores all the intermediate configurations (i.e. requires space $O(S(n) T(n))$.
\end{itemize}
Note that for polytime computations in sublinear space this gives a protocol in which the verifier is sublinear-time. 
\end{abstract}
\end{comment}
% -- END Old abstract --

\section{Introduction}
\input{intro.tex}

\section{Preliminaries}
\input{rp.tex}

%\section{On designing rational proofs as interactive proofs}
%\input{rps_as_ips.tex}


% Rational Proofs for NL 
% Are these better than the ones we have already?? (not round complexity-wise)
\section{Rational Proofs for Nondeterministic Space-Bounded Computations }
\input{boundedspace.tex}

\section{Sequential Composability of our protocol}
\input{proof-seq-comp.tex}

\input{extras.tex}

\section{Conclusions and Open Problems}
We presented a rational proof for languages recognized by non-deterministic space-bounded computation. Our protocol is the first rational proof for a general class of language that does not use circuit representations. Our protocol is secure both in the standard stand-alone notion of rational proof introduced in 
\cite{am} and in the stronger composable version presented in \cite{cg15}. 

Our work leaves open a series of questions
\begin{itemize}
\item What is the relationship between scoring rule based protocols vs weak interactive proofs? Our work and the work in \cite{cg15} seem to indicate that the latter technique is more powerful (our work shows an example of a class of language which is not known to be recognizable using scoring rules, the work in \cite{cg15} shows that scoring rules seem inherently insecure in a composable setting). Is it possible to show, however, that a scoring-rule based protocol can be transformed into a weak interactive proof (without a substantial loss of efficiency) therefore showing that it is enough to focus on the latter?

\item Can we build efficient rational proofs for arbitrary poly-time computations, where the verifier runs in sub-linear, or even in linear, time? Even in the standalone model of \cite{am}?

\item Our proof of sequential composability considers only non-adaptive adversaries, and enforces this condition by the use of timing assumptions. Is it possible to construct protocols that are secure against adaptive adversaries? \textbf{XXX: Deal with next sentences before submitting.} Or is it possible to relax the timing assumption to something less stringent than what is required in our protocol?

\item It would be interesting to investigate the connection between the model of Rational Proofs and the work on Computational Decision Theory in  \cite{halpern2011don}. In particular it would be interesting to look at realistic cost models that could affect the choice of strategy by the prover particularly in the sequentially composable model. 
\end{itemize}




%\section*{Acknowledgement}
%We thank Jesper Buus Nielsen for the insightful discussions that inspired this work.
    
\bibliographystyle{plain}
\bibliography{references}

\end{document}
